---
title: "213-assignment-6.1"
author: "Nathalie Bonnet"
date: 05/14/2026
format: html
---

```{r}
# Load necessary packages
library(tidyverse)
library(DBI)
library(duckdb)
library(dbplyr)
```

```{r}
# Open connection to database
conn <- DBI::dbConnect(duckdb::duckdb(), 
                       dbdir = "database/database.duckdb")
conn
```
```{r}
# List tables
DBI::dbListTables(conn)

# Grab tables needed
personnel <- tbl(conn, "Personnel")
egg_table <- tbl(conn, 'Bird_eggs')
nests <- tbl(conn, 'Bird_nests')

# Look at column names again because I can never remember them
head(nests)
head(egg_table)
head(personnel)

# Join on egg table
egg_table %>% 
  #Join nests on nest id
  left_join(nests, by = "Nest_ID") %>% 
  # Group by observer
  group_by(Observer) %>% 
  # Count eggs by observer
  summarise(total_eggs = n()) %>% 
  # Join again on personnel to match name
  left_join(personnel, join_by(Observer == Abbreviation)) %>% 
  # Select desired columns
  select(total_eggs, Name) %>% 
  # Get top 3 results
  slice_max(order_by = total_eggs, n =3)
```

```{r}
# Close connection so the database can be opened elsewhere
DBI::dbDisconnect(conn, shutdown = TRUE)
```

If you used multiple R statements, did:

-dbplyr create a temporary table? Or did it manage to do everything in one query?

dbplyr managed to do every function in one query. 

Did it limit to the first three rows using an R expression or an SQL LIMIT clause?

I used slice_max(), an R expression to limit to the maximum 3 results in total_eggs. I could have also used arrange(desc()), and taken head(3), but I prefer slice max as a cleaner way to do it. 
